---
title: "Momentum"
author: "Rob Hayward"
date: "18 November 2015"
output: 
  html_document: 
    highlight: tango
    theme: cosmo
    toc: yes
---

##Autocorrelation
This comes from [Quintuitive](http://www.quintuitive.com/2015/11/15/trading-autocorrelation)

```{r, warning=FALSE, message=FALSE, cache = TRUE}
require(quantmod)
spy = getSymbols("SPY", from = "1900-01-01")
spy.rets <- ROC(Ad(SPY), na.pad = F)
aa <- acf(tail(spy.rets, 500), main = "ACF computed over last 500 days")
head(aa)
```
Calculate a confidence level.  See note on *stationarity* in the *Other* folder for the estimation of the confidence intervals for the correlation coefficient  
```{r}
conf.level <- 0.95
conf <- qnorm((1 + conf.level)/2)/sqrt(sum(!is.na(spy.rets)))
```

```{r}
high.acf = function(xx, conf.level = 0.95, lag = 1){
  aa = acf(xx, plot = F)
  conf = qnorm((1 + conf.level)/2)/sqrt(sum(!is.na(xx)))
  if(abs(aa$acf[lag + 1, 1, 1]) > conf) sign(aa$acf[lag + 1, 1, 1]) else 0
}
```
Now test the high autocorrelation function
```{r}
backtest.acf = function(rets, n = 21, conf.level = 0.95, lag = 1, fade = F, 
dates = "2004/2013"){
  aa = na.trim(rollapply(rets, width = n + lag, FUN = high.acf, conf.level = 
  conf.level, lag = lag))
  bb = merge(rets, aa, all = F)
  ind = sign(bb[, 1]*bb[, 2])
  if(fade) ind = -ind
  cc = merge(rets, lag.xts(ind), all = F)
  dd = cc[, 1] * cc[, 2]
  strat = dd[dates]
  n.win = NROW(which(as.numeric(strat) > 0, arr.ind = T))
  n.trades = NROW(which(as.numeric(strat) !=0, arr.ind = T))
  str = paste(round(n.win/n.trades * 100, 2), "% [", n.win, "/", n.trades, "]", 
  sep = "")
  print(str)
}
```
Now test
```{r}
backtest.acf(spy.rets, dates = "2004/2013", fade = T, n = 63)
```

Some profit but not many trades. 

###Quant stackexchange 

This comes from [stack  exchange](http://quant.stackexchange.com/questions/19518/thesis-using-momentum-strategies-in-r-tips-on-good-books-guidelines-etc-on-how).    There is some practice in the momentum.R file. 

The [link to the R-forge page](https://r-forge.r-project.org/R/?group_id=316)


This comes from [qantstrattrader](https://quantstrattrader.wordpress.com/2015/09/03/introduction-to-hypothesis-driven-development-overview-of-a-simple-strategy-and-indicator-hypotheses/). 

Details are in QuantMoment.R
