---
title: "Quantlab"
author: "Rob Hayward"
date: "2 February 2016"
output: html_document
---

###Notes
These notes begin with a [StackOverflow](http://quant.stackexchange.com/questions/22902/r-backtesters-quantstrat-vs-sit?newsletter=1&nlcode=365849%7c1e0c) discussion.  The starting point is this [Willya Kipnis](https://www.youtube.com/watch?v=61_F2fcvrsw) You Tube video. It start with some basis data manipulation. There is also a list of references to blotter in R-bloggers (http://www.r-bloggers.com/search/blotter)[here]. There is an overview of blotter (http://artax.karlin.mff.cuni.cz/r-help/library/blotter/html/00Index.html)[here].  There is a link to (http://www.r-programming.org/papers)[Guy Yollin] and some notes on R and quantmod,  Here is another example of a  (https://r-forge.r-project.org/scm/viewvc.php/pkg/blotter/demo/longtrend.R?view=markup&root=blotter)[MA strategy] 

```{r, message=FALSE, warning=FALSE, cache=TRUE}
require(quantmod)
getSymbols("SPY", from = "2000-01-01", to = "2015-12-31")
head(SPY)
```

This constains the full database of open, high, low close. 

```{r, fig.height=4.6}
library(quantmod)
chart_Series(SPY)
```

It is possible to zoom in and zoom out. 

```{r, fig.heigh=4.6}
zoom_Chart("2008")
```

Or choose a particular part
```{r, fig.height=4.6}
zoom_Chart("2008-01-01::2008-01-31")
```

##Indicators
It is possible to calculate simple indicators in R.  For example, the simple, moving average, 

```{r}
sma <- SMA(x = Cl(SPY), n = 200)
tail(sma)
```

There are a lot of indicators that come from R functions. 

```{r, fig.height=4.6}
chart_Series(SPY)
add_TA(sma, on=1, lwd = 1.5, col = 'blue')
```
```{r,fig.height=4.6}
chart_Series(SPY, subset = "2008-01-01::2009-12-31")
add_TA(sma, on = 1, col = "blue")
```

Add an RSI. 

```{r, fig.height = 4.6}
testRSI <- RSI(Cl(SPY), n = 2)
chart_Series(SPY, subset = "2008-01-01::2009-12-31")
add_TA(testRSI, col = 'green')
```

##Build a trading system
The basis of the trading system will be 

* The close must be above the 200 moving average
* Buy when RSI2 crosses under 10
* Buy again when RSI crosses under 6
* Close when the price closes above the SMA5. 

This is a Larry Connors trading system. 

```{r, fig.height=4.6}
library(quantstrat)
library(IKTrading)
options("getSymbols.warning4.0=FALSE")
rm(list=ls(.blotter), envir = .blotter)
currency('USD')
Symbols = 'SPY'
suppressMessages(getSymbols(symbols, from = "1998-01-01", to = "2012-12-31"))
stock(symbols, currency = 'USD', multiplier = 1)
initDate = "1990-01-01"
tradeSize = 10000
initEq = tradeSize*length(Symbols)

rm.strat(portfolio.st)
rm.strat(strategy.st)
# i this that these go here to make sure that tehre is a clean environemnt.
strategy.st <- portfolio.st <- account.st <- 'RSI_10_6'
# they are all called 'RSI_10_6`
initPortf(portfolio.st, symbols = symbols, initDate=initDate, currency='USD')
initAcct(account.st, portfolios=portfolio.st,initDate = initDate, currency = 'USD', initEq=initEq)
initOrders(portfolio.st, initDate=initDate)
strategy(strategy.st, store = TRUE)

#parameters
nRSI = 2
thresh1 = 10
thresh2 = 6

nSMAexit = 5
nSMAfilter = 200

period = 10
pctATR = 0.02
# This is the trade size.  It is linked to volatility and is designed
# to make sure that the risk is stable. There are larger trades when there
# are larger moves. 
maxpct = 0.04
# indicators
add.indicator(strategy.st, name ="lagATR", 
#lagATR is in the IKTrading library.  It will calculate the ATR and it will 
# lag it so that we have yesterday's ATR to use for today.
              arguments = list(HLC=quote(mktdata)), n = period, 
# ATR will take the high, low close and the label will allow this to be 
# used later.
              label = "atrx")

add.indicator(strategy.st, name = "RSI", 
              arguments = list(price = quote(Cl(mkdata)), n = nRSI), 
                               label = "rsi")
# quantmode convention says that the price must be a 'quote'
add.indicator(strategy.st, name = 'SMA', 
              arguments = list(price = quote(Cl(mkdata)), n = nSMAexit),
              label = 'quickSMA')
add.indicator(strategy.st, name = 'SMA', 
              arguments = list(price = quote(Cl(mkdata)), n = nSMAfilter), 
              label = 'filterMA')
```

###Signals
There are four types of signal that are important

* `sigComparison` compares two values (ie close is above the 200 MA)
* `sigCrossover` looks for a one-time change in a relationship (ie, 2 day MA crosses the 5 day MA)
* `sigThreshold` whether a value is greater or less than a specific value (ie. RSI2 is under 10)
* `sigAND` (from IKTrading) - compare whether both signals are true. The pattern is similar to the strategty. 

```{r, fig.height=5}
add.signal(strategy.st, name = 'sigComparison', 
           arguments = list(column = c('rsi', 'filterMA'), 
           relationship = 'gt'), label = 'pptrend')
# gt stands for greater than.  There are a few of these
add.signal(strategy.st, name = 'sigThreshold', 
           arguments = list(column = 'rsi', threshold = 'thresh1',
                                   relationship = 'lt', cross = FALSE), 
                            label = 'rsiThresh1')
# cross is false because we want a trigger even if there is a 
add.signal(strategy.st, name = 'sigThreshold', 
           arguments = list(column = 'rsi', threshold = 'thresh2',
                            relationship = 'lt', cross = FALSE), 
           label = 'rsiThresh2')
# These strategies only trigger if all the components are true. 
add.signal(strategy.st, name = 'sigAND', 
           arguments = list(columns = c('rsiThresh1', 'upTrend'), 
                            cross = TRUE), label = 'longEntry1')
add.signal(strategy.st, name = 'sigAND',
           arguments = list(columns = c('rsiThresh2', 'upTrend'), 
                            cross = TRUE),
           label = 'longEntry2')
add.signal(strategy.st, name = 'sigCrossover', 
           arguments = list(columns = c('Close', 'quickMA'), 
                            relationship = 'gt'), 
           label = 'exitLonNormal')
add.signal(strategy.st, name = 'sigCrossover', 
           arguments = list(columns = c('close', 'filterMA'), 
                            relationship = 'lt'), 
           label = 'exitLongFilter')
#This is an exit if the close is back below the 200 day MA. 
```

### Rules
There is really only one type of rule.  However, the rules have a whole range of arguments. 

```{r}
add.rule(strategy.st, name = 'ruleSignal', 
         arguments = list(sigcol = 'longEntry1', 
                          sigval = TRUE, 
                          # this will usually be the case
                          ordertype = 'market',
                          #it is possibe to have limit and stop
                          orderside = 'long',
                          replace = FALSE, 
                          # true will overide other rules for the day
                          prefer = 'open',
                          # this it to ensure that you trade after the signal
                          OSFUN = osDollarATR, 
                          # ordersize function.  Can be constant but..
                          # this comes from the IKTrading package
                          # it will look for a ATR column pctATR in our case
                          # and use that to calculate the size of order
                          tradesize = tradeSize,
                          pctATR = pctATR, 
                          maxpctATR = pctATR,
                          # this will limit the size of the overall position
                          atrMod = 'X'), 
         type = 'enter', path.dep = TRUE, label = 'enterLong1')
# this label refers to the label for the signal. 
add.rule(strategy.st, name = 'ruleSignal',
         arguments = list(sfgcol = 'longEntry2', 
                          sigval = TRUE,
                          ordertype = 'long',
                          replace = FALSE, 
                          prefer = 'open',
                          OSFUN = osDollarATR, 
                          tradeSize = tradeSize, 
                          pctATR = pctATR, 
                          maxpcATR = maxpct, 
                          atrMod = 'X'), 
         type = 'enter', path.dep = TRUE, label = 'enterLong2')

add.rule(strategy.st, name = 'ruleSignal', 
         arguments = list(sigcol = 'exitLongNormal', 
                          sigval = TRUE, 
                          orderqty = 'all', 
                          # get rid of all the position
                          # does not try to scale the order
                          ordertype = 'market', 
                          orderside = 'long', 
                          replace = FALSE, 
                          prefer = 'open'), 
         type = 'exit', path.dep = TRUE, label = 'normalExitLong')
# type will just exit.  It is possible to rebalance, but that is not used here

add.rule(strategy.st, name = 'ruleSignal', 
         arguments = list(sigcol = 'exitLongFilter', 
                          sigval = TRUE, 
                          orderqty = 'all',
                          ordertype = 'market',
                          orderside = 'long', 
                          replace = FALSE, 
                          prefer = 'open'), 
         type = 'exit', path.dep = TRUE, label = 'filterExitLong')
# labels are important in quantstrat.  These are not neede dhere but are 
# important if using stock loss. 
```{r}
t1 <- Sys.time()
out <- applyStrategy(strategy = strategy.st, portfolios = portfolio.st)
t2 <- Sys.time()
print(t2-t1)
# set up analytics
updatePortf(portfolio.st)
dateRange <- time(getPortfolio(portfolio.st)$summary)[-1]
updateAcct(portfolio.st, dateRange)
updateEndEq(account.st)
```
##Apply the strategy

```
         
 56.23                         
                          
                          
                          





Quantstrat has its own syntax.    


Book is code complete

````